\textit{Last updated: February 2021}

Department of Atmospheric and Cryospheric Science \\
Research centre for Climate \\
University of Innsbruck \\
Innrain 52f, A-6020 Innsbruck \\
Personal website: \href{https://fabienmaussion.info}{https://fabienmaussion.info}


\section*{Education}
\label{\detokenize{ch08/cv:education}}\begin{itemize}[nosep]
\item {} 
2002: Baccalaureate (High School Diploma)

\item {} 
2003--2004: Maths and physics preparation class in Strasbourg

\item {} 
2005--2006: \href{https://www.isae-supaero.fr/en/}{SUPAÉRO} -- Institut Supérieur de l’Aéronautique et de l’Espace, Toulouse (aerospace engineering school)

\item {} 
2007--2008: \href{https://www.tu.berlin/}{Technische Universität Berlin} -- International exchange year and Master degree

\item {} 
2008--2014: \href{https://www.klima.tu-berlin.de}{Technische Universität Berlin - Chair of Climatology} -- PhD thesis

\end{itemize}

\textbf{PhD Thesis} defended in February 2014 with the title “A new atmospheric dataset for High Asia: development,
validation and applications in climatology and in glaciology” (summa cum laude). 
Supervisor: Dieter Scherer. Reviewers: Christoph Schneider (RWTH Aachen), Georg Kaser (University of Innsbruck)


\section*{Professional experience}
\label{\detokenize{ch08/cv:professional-experience}}\begin{itemize}
\item {} 
2006--2007: Interim year as engineering trainee -- Space mechanics at \href{https://www.c-s.fr}{C-S Group}, Toulouse

\item {} 
2008--2014: PhD / Post-doc at the \href{http://klima.tu-berlin.de}{Chair of Climatology}, Technische Universität Berlin

\item {} 
2014--2015: Post-doc at the Department of Atmospheric and Cryospheric Sciences (\href{https://www.uibk.ac.at/acinn}{ACINN}), Universität Innsbruck

\item {} 
2015--2016: University Assistant at \href{https://www.uibk.ac.at/acinn}{ACINN}, Universität Innsbruck

\item {} 
Since 2016: Assistant professor at \href{https://www.uibk.ac.at/acinn}{ACINN}, Universität Innsbruck

\end{itemize}


\section*{Research projects \& grants}
\label{\detokenize{ch08/cv:research-projects-grants}}
\textbf{As PI (current)}:
\begin{itemize}[nosep]
\item {} 
2021--2024: PROVIDE -- Paris Agreement Overshooting -- Reversibility, Climate Impacts and Adaptation Needs (H2020, 230k\texteuro{})

\item {} 
2019--2022: \href{https://agroclim-huaraz.info/}{AgroClim - Huaraz}, “Water availability and water demand in the Peruvian Andes” (ÖAW, 443k\texteuro{})

\item {} 
2020--2022: \href{https://www.uibk.ac.at/acinn/research/ice-and-climate/projects/scaling\_regional\_sea\_level\_changes.html.en}{Scaling regional sea-level changes with climate forcings} (FWF, Co-PI)

\end{itemize}

\textbf{As PI (completed)}:
\begin{itemize}[nosep]
\item {} 
2018--2021: \href{https://www.uibk.ac.at/acinn/research/ice-and-climate/projects/modelling-glacier-length-changes.html.en}{Modelling glacier length changes in Alps on the base of tree-ring based temperature reconstructions for the last 2500 years} (Universtität Innsbruck, 120k\texteuro{}, Co-PI)

\item {} 
2019--2020: “Glaciers on the Cloud: OGGM-Edu” (University of Innsbruck, 20k\texteuro{})

\item {} 
2018--2019: \href{https://www.uibk.ac.at/acinn/research/ice-and-climate/projects/holocene-climate-variability.html.en}{The Upper Grindelwald Glacier as indicator for Holocene climate variability} (TWF, 10k\texteuro{})

\end{itemize}

\textbf{As employee}:
\begin{itemize}[nosep]
\item {} 
2008--2014: \href{https://www.klima.tu-berlin.de/index.php?show=reg\_klima\_hochasien\_dynrgtip\&lan=en}{DynRG-TIP} -- Dynamic Response of Glaciers on the Tibetan Plateau to Climate Change (DFG)

\item {} 
2011--2014: \href{https://www.klima.tu-berlin.de/index.php?show=reg\_klima\_hochasien\_wet\&lan=en}{WET} -- Variability and Trends in Water Balance Components of Benchmark Drainage Basins on the Tibetan Plateau (BMBF)

\item {} 
2014--2015: \href{https://www.uibk.ac.at/acinn/research/ice-and-climate/projects/glaciation-of-tropical-mountains.html.en}{Multidecadal to Centennial Climate Variability: Assessing the Conditions for the Glaciation of Tropical Mountains} (FWF)

\end{itemize}


\section*{Awards}
\label{\detokenize{ch08/cv:awards}}\begin{itemize}[nosep]
\item {} 
Wilhelm-Lauer-Preis 2014 (Akademie der Wissenschaften und der Literatur, Mainz): Prize for an outstanding,
original dissertation in the field of mountain geography

\end{itemize}


\section*{Functions at the University of Innsbruck}
\label{\detokenize{ch08/cv:functions-at-the-university-of-innsbruck}}\begin{itemize}[nosep]
\item {} 
Deputy speaker (2017-2021) then speaker (2021-) of the Doctoral Programme “\href{https://www.uibk.ac.at/alpinerraum/dps/dp-mountainclimate/}{Mountain Climate and Environment}”

\item {} 
Chair of the “working group on IT and software infrastructure” at \href{https://www.uibk.ac.at/acinn}{ACINN}

\end{itemize}


\section*{Other activities \& services to the community}
\label{\detokenize{ch08/cv:other-activities-services-to-the-community}}\begin{itemize}[nosep]
\item {} 
Co-Chair of the IACS working group: \href{https://cryosphericsciences.org/activities/working-groups/rgi-working-group/}{Randolph Glacier Inventory (RGI) and its role in future glacier monitoring and GLIMS}

\item {} 
Member of the IACS working group: \href{https://cryosphericsciences.org/activities/ice-thickness/}{Glacier ice thickness estimation}

\item {} 
Member of the CLIC working group: \href{http://www.climate-cryosphere.org/mips/glaciermip}{Glacier Model Intercomparison Project}

\item {} 
Scientific editor: \href{https://www.geosci-model-dev.net/}{Geoscientific Model Development} (EGU Journal)

\item {} 
Reviewer: \textit{J. Geophys. Res., J. Hydrometeorol., Int. J. Climatol., J. Hydrol., The Cryosph., J. Glaciol., Hydrol. Earth Syst. Sci., Q.J.R. Meteorol. Soc., Earth Syst. Dynam., …}

\end{itemize}


\section*{Contributions to open source software and open data}
\label{\detokenize{ch08/cv:contributions-to-open-source-software-and-open-data}}\begin{itemize}[nosep]
\item {} 
\href{http://oggm.org}{oggm.org} (2016-present): glacier evolution model

\item {} 
\href{http://edu.oggm.org}{edu.oggm.org} (2019-present): educational platform

\item {} 
\href{http://xarray.pydata.org}{xarray} (2015-2018): array manipulation software

\item {} 
\href{https://salem.readthedocs.io}{salem} (2014-present): map visualization and WRF model analysis software

\item {} 
\href{https://www.klima.tu-berlin.de/HAR}{High Asia Refined analysis (HAR)}: atmospheric dataset

\item {} 
\href{https://rgitools.readthedocs.io/en/latest/dems.html}{RGI-TOPO}: topography dataset for mountain glaciers

\item {} 
…

\end{itemize}


\section*{Teaching}
\label{\detokenize{ch08/cv:teaching}}
\textit{Current teaching load: 8 hours per week in the winter term.}

\textbf{Current classes}
\begin{itemize}[nosep]
\item {} 
\textbf{Introduction to meteorology and climatology}:
\href{https://orawww.uibk.ac.at/public/lfuonline\_lv.details?sem\_id\_in=16W\&lvnr\_id\_in=707606}{fundamentals of the climate system}
for undergraduate students (winter semester, 2hrs).

Topics: components of the
climate system, general circulation of the atmosphere and of the oceans,
climate variability (ENSO, NAO, Monsoon), climate change and climate policy.

\item {} 
\textbf{Physics of the climate system}: \href{https://orawww.uibk.ac.at/public/lfuonline\_lv.details?sem\_id\_in=15W\&lvnr\_id\_in=707712}{advanced course in physical climatology}
for graduate students (winter semester, 3hrs).

Climate variability, synoptic climatology, paleoclimate, climate modelling,
climate change and feedbacks.

The lecture practicals are \href{http://fabienmaussion.info/climate\_system/}{available online}.

\item {} 
\textbf{Scientific Programming}: \href{https://orawww.uibk.ac.at/public/lfuonline\_lv.details?sem\_id\_in=18S\&lvnr\_id\_in=707716}{advanced course in programming}
for graduate students (winter semester, 3hrs).

Modern programming techniques for (geo-)scientists:
numerics, software structure, unit testing, object-oriented programming, version control, open development practices…

The lecture notes are \href{http://fabienmaussion.info/scientific\_programming/}{available online}.

\end{itemize}

Most recent student evaluations (2020/21):
\href{https://fabienmaussion.info/images/teaching/eval/2020WS\_SciPro.pdf}{scientific programming},
\href{https://fabienmaussion.info/images/teaching/eval/2020WS\_PhyClim.pdf}{physics of the climate system},
\href{https://fabienmaussion.info/images/teaching/eval/2020WS\_EKlim.pdf}{Einführung in die Klimatologie}.

\textbf{Past classes}

For a full list of past classes and student evaluations, visit \href{https://fabienmaussion.info/teaching/}{my personal website}.


\section*{Student supervision}
\label{\detokenize{ch08/cv:student-supervision}}

\subsection*{PhD theses (completed)}
\label{\detokenize{ch08/cv:phd-theses-completed}}\begin{itemize}[nosep]
\item {} 
\textbf{Julia Eis} (Universität Bremen, co-supervised, 2020)
: Reconstructing glacier evolution using a flowline model (\href{https://media.suub.uni-bremen.de/handle/elib/4635}{link})

\item {} 
\textbf{Beatriz Recinos} (Universität Bremen, co-supervised, 2020)
: Ocean-glacier interaction on the large regional scale (\href{https://media.suub.uni-bremen.de/handle/elib/4637}{link})

\end{itemize}


\subsection*{Master theses (completed)}
\label{\detokenize{ch08/cv:master-theses-completed}}\begin{itemize}[nosep]
\item {} 
\textbf{Castellani, M.} (ACINN, 2020)
: Estimating Glacier Ice Thickness with Machine Learning (\href{https://diglib.uibk.ac.at/urn:nbn:at:at-ubi:1-60115}{link})

\item {} 
\textbf{Schuster, L.} (ACINN, 2020)
: Response time sensitivity of glaciers using the Open Global Glacier Model (\href{https://diglib.uibk.ac.at/ulbtirolhs/content/titleinfo/4864453}{link})

\item {} 
\textbf{Trichtl, M.} (ACINN, 2020)
: The atmospheric water budget over the Tibetan Plateau in ERA-Interim and ERA5 reanalyses (\href{https://diglib.uibk.ac.at/ulbtirolhs/content/titleinfo/4888002}{link})

\item {} 
\textbf{Hatvan, V.} (ACINN, 2019)
: Evaluation of the physical SNOWPACK model under arctic conditions : An applicability study for the area around Longyearbyen, Svalbard (\href{http://diglib.uibk.ac.at/ulbtirolhs/content/titleinfo/3584652}{link})

\item {} 
\textbf{Gregor, P.} (ACINN, 2019)
: Inversion of Glacier Bed from Surface Observations by Cost Minimization : Introducing the Open Source Model COMBINE (\href{http://diglib.uibk.ac.at/ulbtirolhs/content/titleinfo/3086935}{link})

\item {} 
\textbf{Kilian, M.} (ACINN @ DLR, co-supervised, 2018)
: Impact of the Eruption of Mt. Pinatubo on the chemical composition of the tropical atmosphere as simulated with EMAC

\item {} 
\textbf{Cerny, M.} (ACINN, 2018)
: Lake-level changes on the Tibetan Plateau and their Relation to Glacial Melt (\href{http://diglib.uibk.ac.at/ulbtirolhs/content/titleinfo/2347464}{link})

\item {} 
\textbf{Schlumpberger, M.} (ACINN, 2017)
: Wet and dry spells in the Rio Santa Basin, Peruvian Andes, and connections to the large-scale circulation (\href{http://diglib.uibk.ac.at/urn:nbn:at:at-ubi:1-6985}{link})

\item {} 
\textbf{Siller, M.} (ACINN, 2017)
: WRF simulation of wet and dry spells in the Rio Santa Basin, Peruvian Andes - A WRF Modeling Case Study (\href{http://diglib.uibk.ac.at/urn:nbn:at:at-ubi:1-7816}{link})

\item {} 
\textbf{Thorlaksson, D.} (ACINN, 2017)
: Calibrating a glacier ice thickness model from in-situ point measurements (\href{http://diglib.uibk.ac.at/urn:nbn:at:at-ubi:1-7259}{link})

\item {} 
\textbf{Zier, C.} (ACINN, co-supervised, 2017)
: Wie beeinflussen großskalige Wetterstrukturen das lokale Wetter in den Anden von Chile? Ein Downscaling Experiment (\href{http://diglib.uibk.ac.at/urn:nbn:at:at-ubi:1-7092}{link})

\item {} 
\textbf{Zolles, T.} (ACINN, 2016)
: Uncertainty estimation of a glacier mass balance model (\href{http://diglib.uibk.ac.at/urn:nbn:at:at-ubi:1-5240}{link})

\end{itemize}


\subsection*{Bachelor theses (completed)}
\label{\detokenize{ch08/cv:bachelor-theses-completed}}\begin{itemize}[nosep]
\item {} 
\textbf{Schwienbacher, F.} (ACINN, 2017)
: Model sensitivity of the mass balance module of the \href{http://oggm.org/}{OGGM} model

\item {} 
\textbf{Oberrauch, M.} (ACINN, 2016)
: Calibration and validation of a glacier model applied to the Upper Grindelwald Glacier from 1880 to present

\item {} 
\textbf{Gstir, T.}  (ACINN, 2016)
: Klimasensitivität des Oberen Grindelwaldgletschers untersucht mithilfe des \href{http://oggm.org}{OGGM}

\end{itemize}

For a list of current advisees, visit \href{https://fabienmaussion.info/team/}{my personal website}.


\section*{List of publications}

\begin{footnotesize}
\begin{itemize}[nosep]
\item {} 
Schuster, L., Maussion, F., Langhamer, L. and Moseley, G. E.: Lagrangian detection of precipitation moisture sources
for an arid region in northeast Greenland: relations to the North Atlantic Oscillation, sea ice cover, and temporal
trends from 1979 to 2017, Weather Clim. Dyn., 2(1), 1--17, doi:10.5194/wcd-2-1-2021, 2021.

\item {} 
Marzeion, B., Hock, R., Anderson, B., Bliss, A., Champollion, N., Fujita, K., Huss, M., Immerzeel, W., Kraaijenbrink,
P., Malles, J., Maussion, F., Radić, V., Rounce, D. R., Sakai, A., Shannon, S., Wal, R. and Zekollari, H.:
Partitioning the Uncertainty of Ensemble Projections of Global Glacier Mass Change, Earth’s Futur., 8(7), doi:
10.1029/2019ef001470, 2020.

\item {} 
Pelto, B. M., Maussion, F., Menounos, B., Radić, V. and Zeuner, M.: Bias-corrected estimates of glacier thickness in
the Columbia River Basin, Canada, J. Glaciol., 1--13, doi:10.1017/jog.2020.75, 2020.

\item {} 
Zemp, M., Huss, M., Thibert, E., Eckert, N., McNabb, R., Huber, J., Barandun, M., Machguth, H., Nussbaumer, S. U.,
Gärtner-Roer, I., Thomson, L., Paul, F., Maussion, F., Kutuzov, S. and Cogley, J. G.: Global glacier mass changes and
their contributions to sea-level rise from 1961 to 2016, Nature, 568(7752), 382--386, doi:10.1038/s41586-019-1071-0,
2019.

\item {} 
Recinos, B., Maussion, F., Rothenpieler, T. and Marzeion, B.: Impact of frontal ablation on the ice thickness
estimation of marine-terminating glaciers in Alaska, Cryosph., 13(10), 2657--2672, doi:10.5194/tc-13-2657-2019, 2019.

\item {} 
Maussion, F., Butenko, A., Champollion, N., Dusch, M., Eis, J., Fourteau, K., Gregor, P., Jarosch, A. H., Landmann,
J., Oesterle, F., Recinos, B., Rothenpieler, T., Vlug, A., Wild, C. T. and Marzeion, B.: The Open Global Glacier
Model (OGGM) v1.1, Geosci. Model Dev., 12(3), 909--931, doi:10.5194/gmd-12-909-2019, 2019.

\item {} 
Horak, J., Hofer, M., Maussion, F., Gutmann, E., Gohm, A. and Rotach, M. W.: Assessing the added value of the
Intermediate Complexity Atmospheric Research (ICAR) model for precipitation in complex topography, Hydrol. Earth Syst.
Sci., 23(6), 2715--2734, doi:10.5194/hess-23-2715-2019, 2019.

\item {} 
Eis, J., Maussion, F. and Marzeion, B.: Initialization of a global glacier model based on present-day glacier geometry
and past climate information: an ensemble approach, Cryosph., 13(12), 3317--3335, doi:10.5194/tc-13-3317-2019, 2019.

\item {} 
Zolles, T., Maussion, F., Galos, S. P., Gurgiser, W. and Nicholson, L.: Robust uncertainty assessment of the
spatio-temporal transferability of glacier mass and energy balance models, Cryosph., 13(2), 469--489, doi:
10.5194/tc-13-469-2019, 2019.

\item {} 
Farinotti, D., Huss, M., Fürst, J. J., Landmann, J., Machguth, H., Maussion, F. and Pandit, A.: A consensus estimate
for the ice thickness distribution of all glaciers on Earth, Nat. Geosci., 12(3), 168--173, doi:
10.1038/s41561-019-0300-3, 2019.

\item {} 
Strasser, U., Marke, T., Braun, L., Escher-Vetter, H., Juen, I., Kuhn, M., Maussion, F., Mayer, C., Nicholson, L.,
Niedertscheider, K., Sailer, R., Stötter, J., Weber, M. and Kaser, G.: The Rofental: a high Alpine research basin (
1890--3770 m a.s.l.) in the Ötztal Alps (Austria) with over 150 years of hydrometeorological and glaciological
observations, Earth Syst. Sci. Data, 10(1), 151--171, doi:10.5194/essd-10-151-2018, 2018.

\item {} 
Goosse, H., Barriat, P.-Y., Dalaiden, Q., Klein, F., Marzeion, B., Maussion, F., Pelucchi, P. and Vlug, A.: Testing
the consistency between changes in simulated climate and Alpine glacier length over the past millennium, Clim. Past,
14(8), 1119--1133, doi:10.5194/cp-14-1119-2018, 2018.

\item {} 
Marzeion, B., Kaser, G., Maussion, F. and Champollion, N.: Limited influence of climate change mitigation on
short-term glacier mass loss, Nat. Clim. Chang., 8, doi:10.1038/s41558-018-0093-1, 2018.

\item {} 
Mölg, T., Maussion, F., Collier, E., Chiang, J. C. H. and Scherer, D.: Prominent mid-latitude circulation signature in
High Asia’s surface climate during monsoon, J. Geophys. Res. Atmos., 1--11, doi:10.1002/2017JD027414, 2017.

\item {} 
Galos, S. P., Klug, C., Maussion, F., Covi, F., Nicholson, L., Rieg, L., Gurgiser, W., Mölg, T. and Kaser, G.:
Reanalysis of a 10-year record (2004--2013) of seasonal mass balances at Langenferner/Vedretta Lunga, Ortler Alps,
Italy, Cryosph., 11(3), 1417--1439, doi:10.5194/tc-11-1417-2017, 2017.

\item {} 
Farinotti, D., Brinkerhoff, D. J., Clarke, G. K. C., Fürst, J. J., Frey, H., Gantayat, P., Gillet-Chaulet, F., Girard,
C., Huss, M., Leclercq, P. W., Linsbauer, A., Machguth, H., Martin, C., Maussion, F., Morlighem, M., Mosbeux, C.,
Pandit, A., Portmann, A., Rabatel, A., Ramsankaran, R., Reerink, T. J., Sanchez, O., Stentoft, P. A., Singh Kumari,
S., van Pelt, W. J. J., Anderson, B., Benham, T., Binder, D., Dowdeswell, J. A., Fischer, A., Helfricht, K., Kutuzov,
S., Lavrentiev, I., McNabb, R., Gudmundsson, G. H., Li, H. and Andreassen, L. M.: How accurate are estimates of
glacier ice thickness? Results from ITMIX, the Ice Thickness Models Intercomparison eXperiment, Cryosph., 11(2),
949--970, doi:10.5194/tc-11-949-2017, 2017.

\item {} 
Spiess, M., Schneider, C. and Maussion, F.: MODIS-derived interannual variability of the equilibrium-line altitude
across the Tibetan Plateau, Ann. Glaciol., 57(71), 140--154, doi:10.3189/2016AoG71A014, 2016.

\item {} 
Otto, M., Höpfner, C., Curio, J., Maussion, F. and Scherer, D.: Assessing vegetation response to precipitation in
northwest Morocco during the last decade: an application of MODIS NDVI and high resolution reanalysis data, Theor.
Appl. Climatol., 123(1--2), 23--41, doi:10.1007/s00704-014-1344-3, 2016.

\item {} 
Biskop, S., Maussion, F., Krause, P. and Fink, M.: Differences in the water-balance components of four lakes in the
southern-central Tibetan Plateau, Hydrol. Earth Syst. Sci, 20, 209--225, doi:10.5194/hess-20-209-2016, 2016.

\item {} 
Zhu, M., Yao, T., Yang, W., Maussion, F., Huintjes, E. and Li, S.: Energy- and mass-balance comparison between Zhadang
and Parlung No. 4 glaciers on the Tibetan Plateau, J. Glaciol., 61(227), 595--607, \\ doi:10.3189/2015JoG14J206, 2015.

\item {} 
Spiess, M., Maussion, F., Möller, M., Scherer, D. and Schneider, C.: Modis derived equilibrium line altitude estimates
for purogangri ice cap, tibetan plateau, and their relation to climatic predictors (2001--2012), Geogr. Ann. Ser. A,
Phys. Geogr., 97(3), 599--614, doi:10.1111/geoa.12102, 2015.

\item {} 
Huintjes, E., Sauter, T., Schröter, B., Maussion, F., Yang, W., Kropáček, J., Buchroithner, M., Scherer, D., Kang, S.
and Schneider, C.: Evaluation of a Coupled Snow and Energy Balance Model for Zhadang Glacier, Tibetan Plateau, Using
Glaciological Measurements and Time-Lapse Photography, Arctic, Antarct. Alp. Res., 47(3), 573--590, doi:
10.1657/AAAR0014-073, 2015.

\item {} 
Curio, J., Maussion, F. and Scherer, D.: A 12-year high-resolution climatology of atmospheric water transport over the
Tibetan Plateau, Earth Syst. Dyn., 6(1), 109--124, doi:10.5194/esd-6-109-2015, 2015.

\item {} 
Collier, E., Maussion, F., Nicholson, L. I., Mölg, T., Immerzeel, W. W. and Bush, a. B. G.: Impact of debris cover on
glacier ablation and atmosphere--glacier feedbacks in the Karakoram, Cryosph., 9(4), 1617--1632, doi:
10.5194/tc-9-1617-2015, 2015.

\item {} 
Maussion, F., Gurgiser, W., Großhauser, M., Kaser, G. and Marzeion, B.: ENSO influence on surface energy and mass
balance at Shallap Glacier, Cordillera Blanca, Peru, Cryosph., 9(4), 1663--1683, doi:10.5194/tc-9-1663-2015, 2015.

\item {} 
Mölg, T., Maussion, F. and Scherer, D.: Mid-latitude westerlies as a driver of glacier variability in monsoonal High
Asia, Nat. Clim. Chang., 4(1), 68--73, doi:10.1038/nclimate2055, 2014.

\item {} 
Maussion, F., Scherer, D., Mölg, T., Collier, E., Curio, J. and Finkelnburg, R.: Precipitation Seasonality and
Variability over the Tibetan Plateau as Resolved by the High Asia Reanalysis*, J. Clim., 27(5), 1910--1927, doi:
10.1175/JCLI-D-13-00282.1, 2014.

\item {} 
Dietze, E., Maussion, F., Ahlborn, M., Diekmann, B., Hartmann, K., Henkel, K., Kasper, T., Lockot, G., Opitz, S. and
Haberzettl, T.: Sediment transport processes across the Tibetan Plateau inferred from robust grain-size end members in
lake sediments, Clim. Past, 10(1), 91--106, doi:10.5194/cp-10-91-2014, 2014.

\item {} 
Collier, E., Nicholson, L. I., Brock, B. W., Maussion, F., Essery, R. and Bush, a. B. G.: Representing moisture fluxes
and phase changes in glacier debris cover using a reservoir approach, Cryosph., 8(4), 1429--1444, doi:
10.5194/tc-8-1429-2014, 2014.

\item {} 
Kropacek, J., Maussion, F., Chen, F., Hoerz, S., Hochschild, V. and Kropáček, J.: Analysis of ice phenology of lakes
on the Tibetan Plateau from MODIS data, Cryosph., 7(1), 287--301, doi:10.5194/tc-7-287-2013, 2013.

\item {} 
Collier, E., Mölg, T., Maussion, F., Scherer, D., Mayer, C. and Bush, a. B. G.: High-resolution interactive modelling
of the mountain glacier--atmosphere interface: an application over the Karakoram, Cryosph., 7(3), 779--795, doi:
10.5194/tc-7-779-2013, 2013.

\item {} 
Mölg, T., Maussion, F., Yang, W. and Scherer, D.: The footprint of Asian monsoon dynamics in the mass and energy
balance of a Tibetan glacier, Cryosph., 6(6), 1445--1461, doi:10.5194/tc-6-1445-2012, 2012.

\item {} 
Maussion, F., Scherer, D., Finkelnburg, R., Richters, J., Yang, W. and Yao, T.: WRF simulation of a precipitation
event over the Tibetan Plateau, China -- an assessment using remote sensing and ground observations, Hydrol. Earth
Syst. Sci., 15(6), 1795--1817, doi:10.5194/hess-15-1795-2011, 2011.

\item {} 
Bolch, T., Yao, T., Kang, S., Buchroithner, M. F., Scherer, D., Maussion, F., Huintjes, E. and Schneider, C.: A
glacier inventory for the western Nyainqentanglha Range and the Nam Co Basin, Tibet, and glacier changes 1976-2009,
Cryosph., 4(3), 419--433, doi:10.5194/tc-4-419-2010, 2010.


\end{itemize}
\end{footnotesize}